### 2020-08-14 Analysis/Code/Paper.Rmd
Added .tex to gitignore
Added all review labels to the Julia code

```{r, include=F}
reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos + 
              + noScore + negative + mPositive + realPositive + vPositive + ovPositive +
              log(reviews) + age + poly(tWODisc, degree = 2) + day + week, data = transPanel)
cov<-vcovHC(reg1)
se1 <- sqrt(diag(cov))

star.out.transitions <- stargazer(reg1,
          label = "transitionReg",
          table.placement = "hp",
          header = FALSE,
          title = "Discounts In The Days Around Transition",
          se=list(se1),
          #column.labels=c(),
          dep.var.labels = c("Discount Probability"),
          covariate.labels = c("Days to Transition", "Days After Transition", "No Score", 
                               "Negative", "Mostly Positive", "Positive", "Very Positive",
                               "Ov. Positive", "Log Reviews", "Age", "Const"),
          model.numbers = F,
          omit = c("day", "week", "tWODisc"),
          omit.stat=c("f","adj.rsq","ser"),
          no.space=T)
```

@@

reg3 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
               mPositive + age + young + day + week,
                 data=panel[],
            model="within")
cov<-vcovHC(reg3, method="white1")
se3 <- sqrt(diag(cov))

@@

reg1 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
               mPositive + realPositive + vPositive + age + young + day + week,
                 data=panel[],
            model="within")
cov<-vcovHC(reg1, method="white1")
se1 <- sqrt(diag(cov))

@@

reg2 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
               mPositive + realPositive + vPositive + age + young + day + week,
                 data=panel[],
            model="within")
cov<-vcovHC(reg2, method="white1")
se2 <- sqrt(diag(cov))

star.out <- stargazer(reg1, reg2, reg3,
             label = "potentialTransitionsResults",
             table.placement = "hp",
             header = FALSE,
             title = "Discounts Close to Potential Transitions",
             se=list(se1, se2, se3),
             dep.var.labels = c("Discount Probability"),
             column.labels = c("Full", "1 W. to Tr.", "Simple Tr."),
             covariate.labels = c("Close to Pos. Transition", "Close to Neg. Transition",
                                  "Log Days to Pos. Tr.", "Log Days to Neg Tr.",
                                  "Log Reviews", "Mostly Positive", "Positive",
                                  "Very Positive", "Age", "Age $\\le 14$"),
             model.numbers = F,
             omit = c("day", "week", "tWODisc"),
             omit.stat=c("f","adj.rsq","ser"),
             no.space=T)

@@

```{r results = 'asis'}
cat(star_insert_row(star.out,
                    c("Time Effects: Weekdays, Week &  $\\checkmark$ &  $\\checkmark$ & $\\checkmark$ \\\\",
                      "Game Effects & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\",
                      "Poly($t$ W/O Discount, $d=2$) & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\"),
                    insert.after = c(33,33,33)))
```

@@

```{r results='asis'}
reg1 <- plm(log(number) ~ log(numberLag) + log(price) + noScore +
              negative + mPositive + positive + log(reviews+1) + 
              age + young + discSeason + day,
                 data=panel[price!=0,],
            model="within")

reg2 <- plm(log(number) ~ log(numberLag) + log(price) + noScore + 
              negative + mPositive + realPositive + vPositive + 
              ovPositive + log(reviews+1) + age + young + 
              day + week,
                data=panel[price!=0,],
            model="within")

table <- texreg(res,
                stars = c(0.01, 0.05, 0.1),
                digits = 3,
                custom.model.names = c("NLLS", "Reg", "Full Reg"),
                reorder.coef = c(1, 9, 2, 3, 8, 10, 
                                 4, 5, 6, 7, 11, 12),
                caption = "Estimates of the Demand Parameters",
                caption.above = T,
                label = "demandEstimates")

@@

Thus, the final set of covariates that I use in estimating (\ref{arrivalReg}) are: price, review label, log reviews, two age variables, and a set of day of the week time effects, and a Seasonal Sale dummy. I mentioned in the Identification section that a more simplistic, yet more tractable, alternative to estimating the non-linear model (\ref{arrivalReg}) is given by equation (\ref{logReg})
$$
\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}
$$
\noindent To check whether the omitted covariates could be playing a crucial role, I will report the results of estimaing (\ref{logReg}) both with the ideal set of covariates, and with the covariates used to estimate (\ref{arrivalReg}). The results are presented in Table \ref{demandEstimates}.

@@

```{r results = 'asis'}
cat(star_insert_row(star.out.transitions, c("Time Effects & Weekdays, Week \\\\",
                                "Game Effects & $\\times$ \\\\",
                                "Polynomial($t$ W/O Discount) & $d = 2$ \\\\"), insert.after = c(34,34,34)))
```

@@

# normally, a lag(discNew, 0:7) could be used in the regression formula, but R returns an
# error that I can not debug
reg1 <- plm(new.reviews ~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
                          discNewLag5 + discNewLag6 + discNewLag7 + 
                          negative + mPositive + positive + age + young + day + week,
                          data = panel, model = "within")
cov<-vcovHC(reg1, method="white1")
se1 <- sqrt(diag(cov))

star.out <- stargazer(reg1,
             label = "reviewLag",
             table.placement = "hp",
             header = FALSE,
             title = "Spikes in Reviews After a Discount",
             se=list(se1),
             dep.var.labels = c("New Reviews"),
             covariate.labels = c("Discount 0 Days Ago", "Discount 1 Day Ago",
                                  "Discount 2 Days Ago", "Discount 3 Days Ago",
                                  "Discount 4 Days Ago", "Discount 5 Days Ago", 
                                  "Discount 6 Days Ago", "Discount 7 Days Ago"),
             model.numbers = F,
             omit = c("day","week","negative","mPositive","positive","age", "young"),
             omit.stat=c("f","adj.rsq","ser"),
             no.space=T)
panel[, discNewLag2:=NULL][, discNewLag3:=NULL][, discNewLag4:=NULL][, discNewLag5:=NULL]
panel[, discNewLag6:=NULL][, discNewLag7:=NULL][, new.reviews:=NULL]
```

>>>>

```{r, include=F}
panel[noScore==T, score := 0]
panel[noScore==T, reviews := 0]
reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos + 
             noScore + negative + mPositive + realPositive +
             vPositive + ovPositive + score +
             log(reviews+1) + age + poly(tWODisc, degree = 2) + 
             day + week, data = transPanel)
cov<-vcovHC(reg1)
se1 <- sqrt(diag(cov))

star.out.transitions <- stargazer(reg1,
          label = "transitionReg",
          table.placement = "hp",
          header = FALSE,
          title = "Discounts In The Days Around Transition",
          se=list(se1),
          #column.labels=c(),
          dep.var.labels = c("Discount Probability"),
          covariate.labels = c("Days to Transition", "Days After Transition", "No Score", 
                               "Negative", "Mostly Positive", "Positive", "Very Positive",
                               "Ov. Positive", "Score", "Log Reviews", "Age", "Const"),
          model.numbers = F,
          omit = c("day", "week", "tWODisc"),
          omit.stat=c("f","adj.rsq","ser"),
          no.space=T)
```

@@

reg3 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
              log(needPosDays) + log(needNegDays) + 
              poly(tWODisc, degree = 2) + log(reviews+1) + score + 
              mPositive + age + young + day + week,
                 data=panel[],
            model="within")
cov<-vcovHC(reg3, method="white1")
se3 <- sqrt(diag(cov))

@@

reg1 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + 
               mPositive + realPositive + vPositive + age + young + day + week,
                 data=panel[],
            model="within")
cov<-vcovHC(reg1, method="white1")
se1 <- sqrt(diag(cov))

@@

reg2 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + 
               mPositive + realPositive + vPositive + age + young + day + week,
                 data=panel[],
            model="within")
cov<-vcovHC(reg2, method="white1")
se2 <- sqrt(diag(cov))

star.out <- stargazer(reg1, reg2, reg3,
             label = "potentialTransitionsResults",
             table.placement = "hp",
             header = FALSE,
             title = "Discounts Close to Potential Transitions",
             se=list(se1, se2, se3),
             dep.var.labels = c("Discount Probability"),
             column.labels = c("Full", "1 W. to Tr.", "Simple Tr."),
             covariate.labels = c("Close to Pos. Transition", "Close to Neg. Transition",
                                  "Log Days to Pos. Tr.", "Log Days to Neg Tr.",
                                  "Mostly Positive", "Positive", "Very Positive",
                                  "Score", "Log Reviews", "Age", "Age $\\le 14$"),
             model.numbers = F,
             omit = c("day", "week", "tWODisc"),
             omit.stat=c("f","adj.rsq","ser"),
             no.space=T)

@@

```{r results = 'asis'}
cat(star_insert_row(star.out,
                    c("Time Effects: Weekdays, Week &  $\\checkmark$ &  $\\checkmark$ & $\\checkmark$ \\\\",
                      "Game Effects & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\",
                      "Poly($t$ W/O Discount, $d=2$) & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\"),
                    insert.after = c(35,35,35)))
```

@@

@@

Thus, the final set of covariates that I use in estimating (\ref{arrivalReg}) are: price, review label, log reviews, two age variables, and a set of day of the week time effects, and a Seasonal Sale dummy. I mentioned in the Identification section that a more simplistic, yet more tractable, alternative to estimating the non-linear model (\ref{arrivalReg}) is given by equation (\ref{logReg})
$$
\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}
$$
\noindent To check whether the omitted covariates could be playing a crucial role, I report the results of estimaing (\ref{logReg}) both with the ideal set of covariates, and with the covariates used to estimate (\ref{arrivalReg}). The results are presented in Table \ref{demandEstimates}.

```{r results='asis'}
reg1 <- plm(log(number) ~ log(numberLag) + log(price) +
            discNewLag + discSeason + noScore + negative + 
            mPositive +
            realPositive + vPositive + ovPositive +
            log(reviews+1) + score + age + young + day,
                data=panel[price!=0,],
            model="within")

reg2 <- plm(log(number) ~ log(numberLag) + log(price) +
              discNewLag + noScore + negative + mPositive +
              realPositive + vPositive + ovPositive +
              log(reviews+1) + score + age + young + day + week,
                data=panel[price!=0,],
            model="within")

table <- texreg(res,
                stars = c(0.01, 0.05, 0.1),
                digits = 3,
                custom.model.names = c("NLLS", "Reg", "Ideal Reg"),
                #reorder.coef = c(1, 9, 2, 3, 8, 10, 
                #                 4, 5, 6, 7, 11, 12),
                caption = "Estimates of the Demand Parameters",
                caption.above = T,
                label = "demandEstimates")

Column “NLLS” in table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column “Reg” presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates; finally, column “Full Reg” reports the results of estimating the log-regression with the ideal set of covariates. The parameters that are of main interest are the price elasticity and the review labels semi-elasticities.

The price coefficient estimates display a strong unanimity across all specifications. It is, perhaps, surprising to find the price elasticity of demand to be as low as `r -round(reg1$coefficients[2], 1)`. It is tempting to

@@

```{r results = 'asis'}
cat(star_insert_row(star.out.transitions, c("Time Effects & Weekdays, Week \\\\",
                                "Game Effects & $\\times$ \\\\",
                                "Polynomial($t$ W/O Discount) & $d = 2$ \\\\"), insert.after = c(36,36,36)))
```

@@

# normally, a lag(discNew, 0:7) could be used in the regression formula, but R returns an
# error that I can not debug
reg1 <- plm(new.reviews ~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
                          discNewLag5 + discNewLag6 + discNewLag7 + 
                          negative + mPositive + realPositive + vPositive + ovPositive + score + age + young + day + week,
                          data = panel, model = "within")
cov<-vcovHC(reg1, method="white1")
se1 <- sqrt(diag(cov))

star.out <- stargazer(reg1,
             label = "reviewLag",
             table.placement = "hp",
             header = FALSE,
             title = "Spikes in Reviews After a Discount",
             se=list(se1),
             dep.var.labels = c("New Reviews"),
             covariate.labels = c("Discount 0 Days Ago", "Discount 1 Day Ago",
                                  "Discount 2 Days Ago", "Discount 3 Days Ago",
                                  "Discount 4 Days Ago", "Discount 5 Days Ago", 
                                  "Discount 6 Days Ago", "Discount 7 Days Ago"),
             model.numbers = F,
             omit = c("day","week","negative","mPositive","realPositive",
                      "vPositive", "ovPositive", "score", "age", "young"),
             omit.stat=c("f","adj.rsq","ser"),
             no.space=T)
panel[, discNewLag2:=NULL][, discNewLag3:=NULL][, discNewLag4:=NULL][, discNewLag5:=NULL]
panel[, discNewLag6:=NULL][, discNewLag7:=NULL][, new.reviews:=NULL]
```
